|

### 2025-05-04 doc/presentation.qmd
Presentation template

--- ## Not rendered in this project; to be used as draft
title: |
  | Earnings Management and Investor Protection:
  | Accounting Reading Group - Assignment III
author: "Mel Mzv"
institute: "Humboldt-Universität zu Berlin – Summer 2024"
date: today
fontsize: "9pt"
pdf-engine: xelatex # pdflatex creates rastered fonts
format: 
  beamer:
    slide-level: 3
    number-sections: true
    toc: false
header-includes:
- \usepackage{booktabs} 
- \usepackage{threeparttable}
- \usepackage{graphicx}
- \usepackage{etoolbox}
- \AtBeginEnvironment{verbatim}{\fontsize{7}{7}\selectfont}  # This sets the font size for verbatim environments
- \input{beamer_theme_trr266.sty}
bibliography: references.bib
biblio-style: apsr
---

@@

>>>>

--- ## Draft of a presentation - include it in Makefile if you run it apart paper.qmd too
title: |
  | Earnings Management and Investor Protection:
  | Accounting Reading Group
author: "Mel Mzv"
institute: "Humboldt-Universität zu Berlin – Summer 2025"
date: today
fontsize: "9pt"
pdf-engine: xelatex # pdflatex creates rastered fonts
format: 
  beamer:
    slide-level: 3
    number-sections: true
    toc: false
header-includes:
- \usepackage{booktabs} 
- \usepackage{threeparttable}
- \usepackage{graphicx}
- \usepackage{etoolbox}
- \AtBeginEnvironment{verbatim}{\fontsize{7}{7}\selectfont}  # This sets the font size for verbatim environments
- \input{beamer_theme_trr266.sty}
bibliography: references.bib
biblio-style: apsr
---

@@

This presentation template serves as a standardized framework for thesis works at WiWi faculty, promoting consistency and professionalism in academic presentations.
